The past 7 years of Ph.D. study have been an unforgettable and
invaluable experience for me. I would not have been able to complete
this dissertation without the guidance, support, and efforts of so
many people with whom I have interacted.

First and foremost, I am profoundly grateful to my advisor, Vivek
Srikumar, who has demonstrated how to be an excellent
researcher, advisor, teacher, and friend. He encouraged me to freely
explore and choose my favorite topics to start rather than immediately
following those rising hot topics on deep learning. I always remember
his encouragement during my first seminar talk on Combinatorial
Categorical Grammar~(CCG), for that, I was attracted by a bunch of
books by Mark Steedman. Thanks to this early exploration, I build my
early research interests in compositional semantics. It also
inspired my final dissertation on independent factorization. He always
believed in me and encouraged me in my early dream of building the world's
best AMR Parser. However, I was easily attracted by engineering
details and got stuck in many `local minimum'. I always felt shame
for my unproductive in my early years, but he taught me a lot during my
difficult time. One important lesson is to write more. He always
reminds me to write more papers than codes and pulls me back to think
more about important problems rather than the details. More importantly,
another lesson is to upgrade your weapon when struggling too long. He
urged me archieve the old AMR parser based on feature engineering and
try deep learning on a new task. Such weapon upgrading also made my
early dream come true at last: our AMR parser ranked 1st in MRP'2019
shared task. I am forever grateful for his extremely kind, caring, and
supportive.

I want to thank Ellen Riloff. It is her NLP course leading me into the
NLP field. She named our team~\tquoted{Talking Geckos,}~which won 1st
in the QA challenge~(Fall 2015, NLP Course project). This early course
award also encouraged me for my Ph.D. study. I appreciate her
suggestions and comments on my research work. I am also impressed by
her meticulous scholarship; I believe it will also impact me in my
future career. More importantly, I want to thank Ellen and Vivek for
setting up the great Utah NLP group, my home at the U, and I will miss
this family and the MEB 4130.

It is also my great honor to have Zac Imel, Qingyao Ai, and Yi Zhang on
my dissertation committee. Thank you all for supervising my dissertation
research and providing valuable input. I thank Zac for his tremendous
support in my first interdisciplinary collaboration on psychotherapy
dialogue. I thank Qingyao for his detailed suggestions on my dissertation
proposal, presentation skills, and dissertation writing. I thank Yi for his
mentoring on two fantastic internships in Amazon Lex, and the two
projects eventually led to the important parts of this dissertation.

I have been so lucky to have a good number of friends in Utah NLP
Group, with a special mention to Youngjun Kim, Ashequl Qadir, Haibo
Ding, Xingyuan Pan, Tao Li, Yichu Zhou, Annie Cherkaev, Tianyu Jiang,
Yuan Zhuang, Zhenduo Wang, Vivek Gupta, Maitrey Mehta, Mattia
Medina-Grespan, Ashim Gupta, Nate Stringham, and Tarun Sunkaraneni. I
will never forget the amazing time I had with them.

During my Ph.D., I have done three unforgettable internships at WeChat
AI and AWS AI~(two times in Amazon Lex Team). I thank my mentors
Yik-Cheung Tam, Cheng Niu, Yi Zhang, and Adel Youssef when I worked at
these places. I thank my other collaborators out of my lab: Michael
Tanana, Eric Poitras, Zhiqiang Liu, Zuohui Fu, Shuo Sun, Debjyoti
Paul, Zhimin Li, and others. I immensely enjoyed the collaborations.


I want to thank my parents, Xianhua Cao and Yuanxiang Wang, and my
elder sisters, Wenjuan and Li. When I decided to leave my previous
industrial job and study abroad, they may feel confused, but they gave
me unbending support and constant encouragement. Without them, I
cannot be the current me today. I never know how to pay them back. I
also want to thank my friends, Min Xian and Fei Xu, who make me like
home. I want to thank Xin Yu for her love and support. Without her, I
would not have come to the U and would not continue my research as a
Postdoctoral at CU Boulder.

Last but not least, I would like to acknowledge an NSF Cyberlearning
grant (\#182287) and a GPU gift from NVIDIA Corporation. Their
valuable support helps me to complete this dissertation.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dissertation-main.ltx"
%%% End:
