\section{Impact of Description Styles (Q3)}
\label{sec:sgd:abl-desc}
%As shown in Figure \ref{fig:schema-dst} and the predefined notations
%in \S\ref{sec:chanllenges-in-sgd}, there are three components in the
%schema definitions: services $V$, intents $I$, slots $S$. Based on the
%given description, participators in DSTC8 schema-guided dialog state
%tracking task use different compositions of service/intent/slots
%descriptions. For example, service description was used by the
%official baseline model for intent/slot matching, but not by the
%winning team~\cite{ma2019end}. The diverse design choices also exists
%in slot value matching.  The difference in architecture choice and
%state tracking strategy confounds different dialog state tracking
%models, thus not comparable to discover which composition is the best
%for each tasks. On the other hand,
Previous work on schema-guided dialog~\cite{rastogi2020schema} are
only based on the provided descriptions in \sgdst~dataset. Recent work
on modeling dialog state tracking as reading
comprehension~\cite{gao2019dialog}~only formulate the descriptions as
simple question format with existing intent/slot names, it is unknown
how it performs when compared to other description styles. Moreover,
they only conduct homogeneous evaluation where training and test data
share the same description style. In this section, We also investigate
how a model trained on one description style will perform on other
different styles, especially in a scenario where chat-bot developers
may design their own descriptions. We first introduce different styles
of descriptions in our study, and then we train models on each
description style and evaluate on tests with corresponding homogeneous
and heterogeneous styles of descriptions. Given the best performance
of \CE~shown in the previous section and its popularity in DSTC8
challenges, we adopt it as our model architecture in this section.

\subsection{Benchmarking Styles}
\label{ssec:desc-styles}
For each intent/slot, we describe their functionalities by the
following different descriptions styles:

\Paragraph{\ID} This is the least informative case of name-based
description: we only use meaningless intent/slot identifiers,
e.g. Intent\_1, Slot\_2. It means we don't use description from any
schema component. We want to investigate how a simple identifier-based
description performs in schema-guided dialog modeling, and the
performance lower-bound on transferring to unseen services.

\Paragraph{\NAMEONLY} Using the original intent/slot names in \sgdst
and \multiwoz dataset as descriptions, to show whether name is enough
for schema-guided dialog modeling.

\Paragraph{\QANAMEONLY} This is corresponding to previous
  work by~\citet{gao2019dialog}. For each intent/slot, it generate a
  question to inquiry about the intent and slot value of the
  dialog. For each slot, it simply follows the template '{\it What
    is the value for {\bf slot i}?}'. Besides that, our work also
  extend the intent description by following the template ``{\it Is
    the user intending to {\bf intent j} }".

  \Paragraph{\ORIGIN} The original descriptions in \sgdst and \multiwoz dataset.

  \Paragraph{\QARICH} Different from the \QANAMEONLY, firstly it is
  based on the original descriptions; secondly, rather than always use
  the ``what is" template to inquiry the intent/slot value, We add
  ``what", ``which", ``how many" or ``when" depending on the entity
  type required for the slot.  Same as \QANAMEONLY, we just add
  prefixes as ``Is the user intending to\ldots'' in front of the original
  description. In a sum, this description is just adding question
  format to original description. The motivation of this description is
  to see whether the question format is helpful or not for
  schema-guided dialog modeling.

  To test the model robustness, we also create two paraphrased versions
  \NAMEPARA~and \PARAPHRASE~for \NAMEONLY~and~\ORIGIN~respectively. We
  first use nematus~\cite{sennrich-etal-2017-nematus} to automatically
  paraphrase the description with back translation, from English to
  Chinese and then translate back, then we manually check the
  paraphrase to retain the main
  meaning. Appendix~\ref{sssec:appendices-example-style} shows examples for
  different styles of schema descriptions.

%
%\Paragraph{\CONSTRAINT} To present the intent/slot dependecy
%  relation, add required slots or depended intent after the original
%  description. Multiwoz 2.1 will not support this style, because no
%  dependency information provided in the dataset.

\subsection{Results on Description Styles}
\label{ssec:desc-experiments}
Unlike the composition used in Table \ref{tbl:schema-seq}, we don't
use the service description to avoid its impact. For each style, we
train separate models on 4 subtasks, then we evaluate them on
different target styles. First, Table \ref{tbl:homo-style-results}
summarizes the performance for homogeneous evaluation, while Table
\ref{tbl:squad2-results-question} shows how the question style
description can benefit from SQuAD2 finetuning. Then we also conduct
heterogeneous evaluation on the other styles\footnote{We don't consider
  the meaningless \ID~style due to its bad performance} as shown in
Table \ref{tbl:hete-style-results-sgd}.
%
%Take noncategorical slots subtask on \sgdst as an example, the results
%are summerized in {\bf last three columns} in Table
%\ref{tbl:style-results-sgd}. {\bf 75.63} under {\it self} column in
%{\bf NonCat} means the joint noncategorical accuracy we train the
%model with \NAMEONLY description and evaluate on \NAMEONLY
%description. However, $64.99\pm15.25$ means when we evaluate the
%\NAMEONLY model on two styles \NAMEONLY and \QANAMEONLY in {\it name}
%group, the average performance on {\it name} group is 64.99, while the
%large deviation 15.05 means the \NAMEONLY noncategorical slot model
%cannot perform consistent good on \QANAMEONLY style.  Finally, the
%last cell " in \ORIGIN row, $73.94\pm3.05$ means the model trained on
%\ORIGIN style actually perform good on \ORIGIN, \QARICH, \PARAPHRASE
%description style, the relative small value in standard deviation
%means relatively stable performance on {\it rich} description group.
\begin{table}[!ht]
\begin{center}{
\setlength{\tabcolsep}{2pt}
\begin{tabular}{c|cccc|cc}
  \toprule
  \hline
\multirow{2}{*}{Style\textbackslash{Task}} & \multicolumn{4}{c|}{ \sgdst } & \multicolumn{2}{c}{ \multiwoz }                                                                                                        \\
                                           & \multicolumn{1}{c}{ Intent}   & \multicolumn{1}{c}{Req} & \multicolumn{1}{c}{Cat} & \multicolumn{1}{c|}{NonCat} & \multicolumn{1}{c}{Cat} & \multicolumn{1}{c}{NonCat} \\ \hline
\ID                                        & 61.16                         & 91.48                   & 62.47                   & 30.19                       & 34.25                   & 52.28                      \\ \hline
\NAMEONLY                                  & {\bf 94.24}                   & 98.84                   & 74.01                   & 75.63                       & 53.72                   & 56.18                      \\
\QANAMEONLY                                & 93.31                         & {\bf 98.86}             & 74.36                   & 74.86                       & {\bf 54.19}             & 56.17                      \\ \hline
%\NAMEPARA                                 & 90.76                         &                         &                         &                             &                         &                            \\ \hline
\ORIGIN                                    & 93.01                         & 98.55                   & 74.51                   & 75.76                       & 52.19                   & 57.20                      \\
\QARICH                                    & 93.42                         & 98.51                   & {\bf 76.64}             & {\bf 76.60}                 & 53.61                   & {\bf 57.80}                \\
%\PARAPHRASE                                & 93.57                         & 98.43                   & 75.79                   & 71.94                       & 51.2                    & 56.52                      \\ \hline
  \hline
  \bottomrule
\end{tabular}
}
\end{center}
\caption{\label{tbl:homo-style-results} Homogeneous evaluation results
  of different description style on \sgdst dataset and \multiwoz
  datasets. The middle horizontal line separate the two name-based
  descriptions and two rich descriptions in our settings. All
  numbers in the table are mixed performance including both seen and
  unseen services.}
\end{table}

\subsubsection{Homogeneous Evaluation}
\label{sssec:homo-eval}
\QParagraph{Is name-based description enough} As shown in Table
\ref{tbl:homo-style-results}, \ID~is the worst case of using name
description, its extremely bad performance indicates name-based
description can be very unstable. However, we found that simple
meaningful name-based description actually can perform the best in
\IC~and~\RSI task, and they perform worse on \CSL~and~\NSL tasks
comparing to the bottom two {\it rich} descriptions. \footnote{Only
  exception happens in \CSL~on \multiwoz. When creating
  \multiwoz~\cite{zang-etal-2020-multiwoz}, the slots with less than
  50 different slot values are classified as categorical slots, which
  leads to inconsistencies. We put detailed discuss about \multiwoz~in
  the supplementary material} After careful analysis on the intents in
\sgdst datasets, we found that most services only contains two kinds
of intents, an information retrieval intent with a name prefix
"Find-", "Get-", "Search-"; another transaction intent like "Add-",
"Reserve-" or "Buy-". Interestingly, we found that all the intent
names in the original schema-guided dataset strictly follows an
action-object template with a composition of words without
abbreviation, such as "FindEvents", "BuyEventTickets". This simple
name template is good enough to describe the core functionality of an
intent in \sgdst dataset.~\footnote{This action-object template has
  also been found efficient for open domain intent induction
  task\cite[e.g.,][OPINE]{vedula2020open}.} Additionally, \RSI is a
relaitively simper task, requesting information are related to
specifial attributes, such as "has\_live\_music", "has\_wifi", where
keywords co-occured in the slot name and in the user utterance, hence
rich explanation cannot help further. On the other side, {\it rich}
descriptions are more necessary for \CSL~and~\NSL task. Because in
many cases, slot names are too simple to represent the functionalities
behind it, for example, slot name "passengers" cannot fully represent
the meaning "number of passengers in the ticket booking".

\QParagraph{Does question format help} As shown in Table
\ref{tbl:homo-style-results}, when comparing row \QARICH~v.s.~\ORIGIN,
we found extra question format can improve the performance on \CSL~and
\NSL task on both \sgdst and \multiwoz~datasets, but not for \IC~and
\RSI tasks. We believe that question format helps the model to focus
more on specific entities in the dialog history. However, when adding
a simple question pattern to \NAMEONLY, comparing row \QANAMEONLY~and
\NAMEONLY, there is no consistent improvement on both of the two
datasets. Further more, we are curious about whether BERT finetuned on
SQuAD2~(SQuAD2-BERT) can further help on the question format. Because
\NSL~are similar with span-based question answering, we focus on
\NSL~here. Table \ref{tbl:squad2-results-question} shows that, after
applying the supplementary training on
SQuAD2~(\S\ref{sec:sup-training}), almost all models get improved on
unseen splits however slightly dropped on seen services. Moreover,
comparing to \QANAMEONLY, \QARICH~is more similar to the natural
questions in the SQuAD2, we obverse that \QARICH~gains more than
\QANAMEONLY~from pretrained model on SQuAD2.

\begin{table}[!t]
\begin{center}{
\setlength{\tabcolsep}{3pt}
\begin{tabular}{c|ccc|ccc}
  \toprule
  \hline
                         \multirow{2}{*}{Style/Dataset} & \multicolumn{3}{c}{\sgdst}  & \multicolumn{3}{c}{\multiwoz}  \\ \cline{2-7}
                                                        & all   & seen  & unseen      & all   & seen  & unseen      \\ \hline
 \multirow{1}{*}{\ORIGIN}                               & +1.99 & -1.79 & {\bf +3.25} & +1.93 & -2.21 & {\bf +4.27} \\ \
 \multirow{1}{*}{\QARICH}                               & +6.13 & -2.01 & {\bf +8.84} & +1.06 & -1.28 & {\bf +3.06} \\ \hline
 \multirow{1}{*}{\NAMEONLY}                             & -0.45 & -1.49 & -0.11       & +1.75 & +0.58 & {\bf +1.77}       \\
 \multirow{1}{*}{\QANAMEONLY}                           & +0.05 & -2.98 & {\bf +1.04} & -0.04 & -0.32 & {\bf +1.25} \\ \hline
  \bottomrule
\end{tabular}
}
\end{center}
\caption{\label{tbl:squad2-results-question} Performance changes when
  using BERT finetuned on SQuAD2 dataset to further finetuning on our
  \NSL~task. }
\end{table}


\subsubsection{Heterogeneous}
\label{sssec:heter-eval}
In this subsection, we first simulate a scenario when there is no
recommended description style for the future unseen services. Hence,
unseen services can follow any description style in our case. We
average the evaluation performance on three other descriptions and
summarized in Table \ref{tbl:hete-style-results-sgd}. The $\Delta$ column
shows the performance change compared to the homogeneous
performance. It is not surprising that almost all models perform worse
on heterogeneous styles than on homogeneous styles due to different
distribution between training and evaluation. The bold number shows
the best average performance on heterogeneous evaluation for each
subtask. The trends are similar with the analysis in homogeneous
evaluation~\ref{sssec:homo-eval}, the name-based descriptions perform
better than other rich descriptions on intent classification
tasks. While on other tasks, the \ORIGIN~description performs more
robust, especially on \NSL~task.

Furthermore, we consider another scenario where fixed description
convention such as \NAMEONLY~and \ORIGIN~are suggested to developers,
they must obey the basic style convention but still can freely use
their own words, such as abbreviation, synonyms, adding extra
modifiers. We train each model on \NAMEONLY~and~\ORIGIN, then evaluate
on the corresponding paraphrased version respectively. In the last two
rows of Table \ref{tbl:hete-style-results-sgd}, the column `para'
shows performance on paraphrased schema, while $\Delta$ shows the
performance change compared to the homogeneous evaluation.
\ORIGIN~still performs more robust than \NAMEONLY~when schema
descriptions get paraphrased on unseen services.
%\footnote{More results
%  and qualitative analysis are availible in the
%  appdendix~\ref{ssec:more-desc-results}.}.

\begin{table}[!ht]
\begin{center}{\scriptsize
\setlength{\tabcolsep}{1pt}
\begin{tabular}{c|c|c|c|c|c|c|c|c}
  \toprule
  \hline
\multirow{3}{*}{Style\textbackslash{Task}} & \multicolumn{8}{c}{ \sgdst }                                                                                                                                                 \\ \cline{2-9}
                                           & \multicolumn{2}{c|}{ Intent(Acc)} & \multicolumn{2}{c|}{Req(F1)} & \multicolumn{2}{c|}{Cat(Joint Acc)} & \multicolumn{2}{c}{NonCat(Joint Acc)}                               \\ \cline{2-9}
                                           & mean                              & $\Delta$                          & mean                                & $\Delta$         & mean        & $\Delta$         & mean        & $\Delta$         \\ \hline
\NAMEONLY                                  & 82.47                             & -11.47                       & 96.92                               & -1.64       & 61.37       & -5.54       & 56.53       & -14.68      \\
\QANAMEONLY                                & {\bf 93.27}                       & +0.58                        & {\bf 97.88}                         & -0.76       & 68.55       & +2.63       & 62.92       & -6.30       \\
\ORIGIN                                    & 79.47                             & -12.70                       & 97.42                               & -0.74       & {\bf 68.58} & -0.3        & {\bf 66.72} & -3.11       \\
\QARICH                                    & 84.57                             & -8.24                        & 96.70                               & -1.45       & 68.40       & -2.89       & 56.17       & -15.00      \\
  \hline
                                           & para                              & $\Delta$                          & para                                & $\Delta$         & para        & $\Delta$         & para        & $\Delta$         \\ \hline
\NAMEONLY                                  & {\bf 92.22}                       & -1.74                        & 97.69                               & -0.87       & 67.39       & -0.7        & 67.17       & -4.04       \\
\ORIGIN                                    & 91.54                             & {\bf -0.63}                  & {\bf 98.42}                         & {\bf +0.26} & {\bf 71.74} & {\bf +2.86} & {\bf 67.68} & {\bf -2.16} \\ \hline
  \bottomrule
\end{tabular}
}
\end{center}
\caption{\label{tbl:hete-style-results-sgd} Results on unseen service with heterogeneous description styles on \sgdst dataset. More results and qualitative analysis are in the appendix~\ref{sec:sgd:more-desc-results}}
\end{table}

%We first consider the diverse description
%within the same {\it name} or {\it rich} group. Within {\it name}
%group, models trained on \NAMEONLY~shows larger standard deviation,
%which indicating unsafe performance of just using simple name as
%description. Moreover, imaging an extremely bad name convention as
%{\bf ID} in section \ref{sssec:com-desc}, the model will lose
%transferbility on unseen service. Within {\it rich} group, we found
%our model trained on \PARAPHRASE~may perform worse than models trained
%on \ORIGIN~and~ \QARICH, because \PARAPHRASE~contains more
%perturbation on \ORIGIN~descriptions, although keeping the same
%meaning. This indicates BERT may fail to retain the similar
%representation for the perturbed sentence with the same meaning.
%Beside the intra-group evaluation, we also consider the inter-group
%hetergenuous evaluation. It is curious whether the model trained on
%{\it rich} description can still retain good performance on simple
%name-based description. We found this only happens on requested slot
%and categorical slot tasks, while on other subtasks, the performance
%dropped drastically. The performance drop is more significant on this
%task requires token-level representation predict the start and end
%position of the slot value, hence we believe this token-level tasks is
%more senstive than sentence-level tasks that depending on a summerized
%sentence representation.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../thesis-main.ltx"
%%% End:
