\todo{adding a summary for this chapter}
The design and implementation of broad-coverage and linguistically
motivated meaning representation frameworks for natural language is
attracting growing attention in recent years. With the advent of deep
neural network-based machine learning techniques, we have made
significant progress to automatically parse sentences intro structured
meaning representation~\cite{Oep:Kuh:Miy:14,Oep:Kuh:Miy:15,May:2016wc,hershcovich-etal-2019-semeval}. Moreover,
the differences between various representation frameworks has a
significant impact on the design and performance of the parsing
systems.

Due to the abstract nature of semantics, there is a diverse set of
meaning representation frameworks in the literature~\cite{abend2017state}. In some
application scenario, tasks-specific formal representations such as
database queries and arithmetic formula have also been proposed. However,
primarily the study in computational semantics focuses on frameworks
that are theoretically grounded on formal semantic theories, and
sometimes also with assumptions on underlying syntactic structures.

Anchoring is crucial in graph-based meaning representation
parsing. Training a statistical parser typically starts with a
conjectured alignment between tokens/spans and the semantic graph
nodes to help to factorize the supervision of graph structure into
nodes and edges. In our paper, with evidence from previous research on
AMR
alignments~\cite{Pourdamghani:2014aligning,Flanigan:2014vc,Wang:2017vt,chen2017unsupervised,szubert2018structured,lyu2018amr}, we propose a uniform handling of three meaning
representations from \texttt{Flavor-0} (DM, PSD) and \texttt{Flavor-2}
(AMR) into a new group referred to as the \textbf{lexical-anchoring}
MRs. It supports both explicit and implicit anchoring of semantic
concepts to tokens.  The other two meaning representations from
\texttt{Flavor-1} (EDS, UCCA) is referred to the group of
\textbf{phrasal-anchoring} MRs where the semantic concepts are
anchored to phrases as well.
/todo{adding more about the contributions}
%
%To support the simplified taxonomy, we named our parser as
%LAPA~({\textbf{L}exical-\textbf{A}nchoring and
%  \textbf{P}hrasal-\textbf{A}nchoring)\footnote{The code is available
%    online at \url{https://github.com/utahnlp/lapa-mrp}}. We proposed a
%    graph-based parsing framework with a latent-alignment mechanism to
%    support both explicit and implicit lexicon anchoring. According to
%    official evaluation results, our submission for this group ranked
%    1st in the AMR subtask, 6th on PSD, and 7th on DM respectively,
%    among 16 participating teams. For phrasal-anchoring, we proposed a
%    CKY-based constituent tree parsing algorithm to resolve the anchor
%    in UCCA, and our post-evaluation submission ranked 5th on UCCA
%    subtask.